---
title: "Simulation 2"
author: "Camille Carter"
date: "2023-02-15"
output: html_document
---
Libraries
```{r}
# load the libraries
library(readxl)
library(quantmod)
library(graphics)
library(ks)
library(stats)
library(EnvStats)
library(gtools)
library(triangle)
library(car)
library(tidyverse)

```

Notes:
- Keep Caluations the same 

What we are ultimately trying to simulate: 
- Cost of a single dry well
- Net Present Value (NPV) of a Single Wet Well

Given Information:
- Drilling Cost 
- Seismic Cost *Dependent on # of wells
- Lease Cost *Dependent on # of wells
- Completion Cost
- Labor/Overhead Costs 
- Inital Production **Correlated
- Decline Rate **Correlated
- Price Projections of oil 
- Net Revenue Interest ie revenue after royalties
- Operating Costs
- Severence Taxes (on final post NRI profit)

Initial thoughts on dry well costs 
- Seismic Cost
- Lease Cost 
- Labor/Overhead Costs 
- Drilling Cost

Initial thoughts on wet well NPV (Essentially calculating Final Net Revenues)
- Initial Costs 
  - Seismic Cost *Dependent on # of wells
  - Lease Cost *Dependent on # of wells
  - Completion Costs 
- Final Net Revenues = Net Value Interest - Costs 
  - Net Value Interest
    - Percentage(kept)
    - Oil Price
    - Annual Production 
      - IP
      - Decline Rate 
  - Recurring Costs 
    - Labor/Overhead Costs
    - Drilling Costs
    - Operating Costs 
    - Severence Taxes


Data Load/Cleaning 
```{r}

#load data
df <- read_excel("Analysis_Data.xlsx", sheet = "Drilling Cost", skip = 2)
price_df <- read_excel("Analysis_Data.xlsx", sheet = "Price Projections", skip = 2)
price_df <- as.data.frame(price_df)
# Check the datatypes of the dataframe
str(df)

# Convert character to numeric variable
char_column <- df$`Arithmetic Return - Crude Oil`
non_numeric <- which(is.na(as.numeric(char_column)) & is.character(char_column))
char_column[non_numeric] <- 0
df$`Arithmetic Return - Crude Oil` <- as.numeric(char_column)

char_column <- df$`Arithmetic Return - Natural Gas`
non_numeric <- which(is.na(as.numeric(char_column)) & is.character(char_column))
char_column[non_numeric] <- 0
df$`Arithmetic Return - Natural Gas` <- as.numeric(char_column)

char_column <- df$`Arithmetic Return - Dry Well`
non_numeric <- which(is.na(as.numeric(char_column)) & is.character(char_column))
char_column[non_numeric] <- 0
df$`Arithmetic Return - Dry Well` <- as.numeric(char_column)


# Taking the average of Nominal Cost and Arithmetic Return
df$average_nominalcost <- rowMeans(df[, c("U.S. Nominal Cost per Crude Oil Well Drilled (Thousand Dollars per Well)",
                                          "U.S. Nominal Cost per Natural Gas Well Drilled (Thousand Dollars per Well)",
                                          "U.S. Nominal Cost per Dry Well Drilled (Thousand Dollars per Well)")])
df$average_arithmeticreturn <- rowMeans(df[, c("Arithmetic Return - Crude Oil", 
                                               "Arithmetic Return - Natural Gas",
                                               "Arithmetic Return - Dry Well")])

# Extract data between 1990 and 2006
subset_df <- subset(df, Date >= as.POSIXct("1990-06-30") & Date <= as.POSIXct("2006-06-30"))

# 2006 to 2023
n = 100000 #number of simulations to run parameter
mu_ar = mean(subset_df$average_arithmeticreturn)
sd_ar = sd(subset_df$average_arithmeticreturn)

P_06 <- last(subset_df$average_nominalcost) # Initial Price in 2006
n_23    <- rep() # Normal Distribution for 2023

set.seed(626)
for(i in 1:n) {
  # 6 values for 2007 to 2012 from the Normal Distribution
  P_07_12_n   <- 1 + rnorm(n=6, mean=mu_ar, sd=sd_ar) 
  
  # 3 decreasing values for 2012 to 2015 from Triangular distribution 
  P_12_15 <- 1 + rtriangle(n=3, a=-0.22, b=-0.07, c=-0.0917) 
  
  # 8 values for 2012 to 2015 from Triangular distribution
  P_15_23 <- 1 + rtriangle(n=8, a=0.02, b=0.06, c=0.05) # Triangular distribution for 2015 to 2023
  
  # Normal Distribution output for 2023
  P_23_n = P_06 * prod(P_07_12_n) * prod(P_12_15) * prod(P_15_23)
  n_23 <- append(n_23, P_23_n) 
}

```

Dry Well Estimation 
```{r}

n = 10000
dw_sim <- rep() # Dry Well Simulation

set.seed(626)

for(i in 1:n) {

  # leased acres per well; cost is $960 
  lease <- rnorm(n=1, mean=600, sd=50) * 960 
  
  # leased acres per well; cost is $43000 
  seismic <- rnorm(n=1, mean=3, sd=0.35) * 43000
  
  # Labor costs Triangular distribution
  labor <- rtriangle(n=1, a=172000, b=279000, c=215000) 
  
  #drilling costs - not sure about this calculation (in millions of dollars)
  drilling <- sample(n_23, 1) * 1000
  
  #Total Costs 
  tot_cost <- lease + seismic + labor + drilling
  dw_sim <- append(dw_sim, tot_cost)

}

# Dry Wells Histogram
hist(dw_sim, breaks=50, main='Single Dry Well Cost', xlab='Cost (in Dollars)')

```

Net Present Value of a Single Wet Well
```{r}

n = 10000

#Initial Costs 
ic_sim <- rep() 

set.seed(626)
for(i in 1:n) {
  # leased acres per well; cost is $960 
  lease <- rnorm(n=1, mean=600, sd=50) * 960 
  
  # leased acres per well; cost is $43000 
  seismic <- rnorm(n=1, mean=3, sd=0.35) * 43000
  
  #drilling costs - not sure about this calculation (in millions of dollars)
  drilling <- sample(n_23, 1) * 1000
  
  #completion costs - only for wet wells 
  completion <- rnorm(n=1, mean=390000, sd=50000) 
  
  #Total Costs 
  tot_cost <- lease + seismic + drilling + completion
  ic_sim <- append(ic_sim, tot_cost)
}

# #  - Net Value Interest
#     - Percentage(kept)
#     - Oil Price
#     - Annual Production 
#       - IP
#       - Decline Rate 

#Correlating IP and Decline Rate 
Value.r.bal <- rep(0,10000)
R <- matrix(data=cbind(1,0.64, 0.64, 1), nrow=2)
U <- t(chol(R))

standardize <- function(x){
  x.std = (x - mean(x))/sd(x)
  return(x.std)
}

destandardize <- function(x.std, x){
  x.old = (x.std * sd(x)) + mean(x)
  return(x.old)
}

m <- 420
s <- 120
location <- log(m^2 / sqrt(s^2 + m^2))
shape <- sqrt(log(1 + (s^2 / m^2)))
print(paste("location:", location))
print(paste("shape:", shape))

#Create 10000 IP from lognorm 
set.seed(626)
IP <- rlnorm(n, location, shape)

#Decline rate, uniform between 15% and 32%
set.seed(626)
DR <- runif(n, min = .15, max = .32)

both <- cbind(standardize(IP), standardize(DR))
both_temp <- U %*% t(both)
both_temp <- t(both_temp)
  
#Correlated IP and Decline Rates (10,000)
#same across the same well
cor_final <- cbind(destandardize(both_temp[,1], IP), destandardize(both_temp[,2], DR))
cor_final <- as.data.frame(cor_final)

######################
#                    #
# Start Calculation  #
#                    #
######################

sim <- 10000
NPV_sim <- rep()
for(i in 1:sim) {
  #Calculate production risk for one year 
  rate_combination <- sample_n(cor_final, 1) #randomly pick one set of rates
  decline_rate <- rate_combination[1,2]
  year_start <- rate_combination[1,1] 
  total_oil <- rep()
  
  for(i in 1:15) {
    year_end <- (1 - decline_rate) * year_start 
    year_oil <- ((year_start + year_end)/2) * 365 
    year_start <- year_end
    total_oil <- append(total_oil, year_oil) #one well 
  }
  
  #Calculate projected price in dollars using triangle distribution 
  total_price <- rep()
  
  for(i in 1:15) {
    min = price_df[i, 'Low Oil Price']
    max = price_df[i, 'High Oil Price']
    avg = price_df[i, 'AEO2021 Reference']
    price <- rtriangle(n=1, a=min, b=max, c=avg)
    total_price <- append(total_price, price)
  }
  
  #Net Revenue Interest
  NRI <- rnorm(n=1, mean=0.75, sd=0.02)
  
  #Severance Tax
  ST = 1 - 0.046
  
  #Annual Revenue for 15 years for one well  
  annual_revenue <- total_oil * total_price * NRI *ST 
    
  #Calculate Reoccuring Costs 
    # - Recurring Costs 
    #   - Labor/Overhead Costs
    #   - Drilling Costs
    #   - Operating Costs 
    #   - Severence Taxes
  
  variable_costs <- rep()

  for(i in 1:15) {
    
    # labor costs Triangular distribution
    labor <- rtriangle(n=1, a=172000, b=279000, c=215000) 
    
    #operating costs (in dollars)
    operating <- rnorm(n=1, mean=2.25, sd=0.3) * total_oil[i] 
    
    #total variable costs 
    tot_cost <- labor + operating 
    variable_costs <- append(variable_costs, tot_cost)
  }
  
  FNR <- annual_revenue - variable_costs
  
  #Calculate Final NRP
  NPV_variables <- rep()
  for(i in 1:15) {
  NPV_variable <- ((FNR[i])/((1 + .10)^i)) #for one year 
  NPV_variables <- append(NPV_variables, NPV_variable)
  }

#sum fractions and subtract inital costs   
NPV <- sum(NPV_variables) - sample(ic_sim, 1) 
NPV_sim <- append(NPV_sim, NPV) 

}

#Plot Net Present Value
hist(NPV_sim, breaks=50, main='Wet Well Net Present Value', xlab='Estimated NPV Value')
summary(NPV_sim)

```


